---
title: "kmean clustering"
author: "Norihito Nakata"
date: "11/14/2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
subtitle: Assignment of Developing Data Product course in coursera
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## K-means clustering

<https://en.wikipedia.org/wiki/K-means_clustering>
k-means clustering aims to partition n observations into k clusters in which each observation belongs to the cluster with the nearest mean, serving as a prototype of the cluster.

I made an easy application where you can try k-means clustering by using random sample dataset. <https://norihiton.shinyapps.io/kmean_clustering/>

## Create sample dataset

- Set seed
```{r echo = TRUE}
set.seed(1234) # select seed
```
- Create 2-D random dataset
```{r echo = TRUE}
x <- c(rnorm(100, 0, 1), rnorm(100, 1, 3), rnorm(100, -1, 4))
y <- c(rnorm(100, -1, 2), rnorm(100, 0, 5), rnorm(100, 1, 1))
data <- data.frame(x, y)
```

## k-means clustering

```{r echo = TRUE}
kCluster <- 5 # select the number of clustering
clusters <- kmeans(data, kCluster)
clusters
```

## Plot the result
```{r}
palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
          "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))
par(mar = c(5.1, 4.1, 0, 1))
```
```{r echo = TRUE}
plot(data,
     col = clusters$cluster,
     pch = 20, cex = 2)
points(clusters$centers, pch = 4, cex = 1.5, lwd = 4)
```

